Ecuador plant species GIFT data

### 2023-03-23 archive/L0_Ecuador_plants_GIFT.Rmd

# Load required packages
```{r}
#run first time only
#remotes::install_github("https://github.com/BioGeoMacro/GIFT",dependencies = TRUE)
library(GIFT)
library(mde)
library(DataExplorer)
library(summarytools)
```

>>>>

# Load required packages
```{r}
remotes::install_github("https://github.com/BioGeoMacro/GIFT",dependencies = TRUE)
library(GIFT)
library(mde)
library(DataExplorer)
library(summarytools)
```
